Import and Tidy ADFG Supplied Location and Haul-out Data

### 2021-05-17 data_raw/adfg/adfg_tidydata.Rmd
PROGRESS WITH ADFG DATA

```{r}
adfg_deployments <- adfg_deployments %>% 
  dplyr::rename(deployid = DeployIDs,
                mapid = MapID,
                date_tagged = DateTagged,
                primary_tag_type = PrimaryTagType,
                flipper_tag_type = FlipperTagType
                ) %>% 
  dplyr::rename_all(tolower) %>% 
  dplyr::mutate(species = tolower(species),
                age = tolower(age),
                sex = tolower(sex)) %>% 
  tidyr::gather(tag_position, tag_type, c(primary_tag_type,flipper_tag_type)) %>% 
  dplyr::mutate(tag_position = ifelse(tag_position == "primary_tag_type",
                   "primary","flipper")) %>% 
  dplyr::filter(!is.na(tag_type)) %>% 
  dplyr::arrange(date_tagged,deployid)

@@

```{r}
adfg_locations <- adfg_locations %>% 
  dplyr::rename(deployid = DeployID,
                location_quality = LocationQuality,
                date_time = Date,
                tag_type = TagType) %>% 
  dplyr::filter(location_quality != "Z") %>% 
  dplyr::select(-MonthNumb) %>% 
  dplyr::rename_all(tolower)

@@

locs_sf <- adfg_locations %>% 
  dplyr::left_join(adfg_deployments, by = c("deployid","tag_type")) %>% 
  sf::st_as_sf(coords = c("longitude","latitude")) %>% 
  sf::st_set_crs(4326) %>% sf::st_transform(3571)

>>>>

```{r}
adfg_deployments <- adfg_deployments %>% 
  dplyr::rename(speno = DeployIDs,
                mapid = MapID,
                date_tagged = DateTagged,
                primary_tag_type = PrimaryTagType,
                flipper_tag_type = FlipperTagType
                ) %>% 
  dplyr::rename_all(tolower) %>% 
  dplyr::mutate(species = tolower(species),
                age = tolower(age),
                sex = tolower(sex)) %>% 
  tidyr::gather(tag_position, tag_type, c(primary_tag_type,flipper_tag_type)) %>% 
  dplyr::mutate(tag_position = ifelse(tag_position == "primary_tag_type",
                   "primary","flipper"),
                deployid = paste(speno,tag_type, sep = "_")) %>% 
  dplyr::relocate(deployid, .after = mapid) %>% 
  dplyr::filter(!is.na(tag_type)) %>% 
  dplyr::arrange(date_tagged,deployid)

@@

```{r}
adfg_locations <- adfg_locations %>% 
  dplyr::rename(speno = DeployID,
                location_quality = LocationQuality,
                date_time = Date,
                tag_type = TagType) %>% 
  dplyr::filter(location_quality != "Z") %>% 
  dplyr::select(-MonthNumb) %>% 
  dplyr::rename_all(tolower) %>% 
  dplyr::mutate(deployid = paste(speno,tag_type, sep = "_")) %>% 
  dplyr::relocate(deployid)

@@

locs_sf <- adfg_locations %>% 
  dplyr::left_join(adfg_deployments, by = c("deployid","speno","tag_type")) %>% 
  sf::st_as_sf(coords = c("longitude","latitude")) %>% 
  sf::st_set_crs(4326) %>% sf::st_transform(3571)
